Immutable Source-Mapped Abstract Syntax Tree:\ \, \\ A Design Pattern for Refactoring Engine APIs

### 2017-09-27 paper.tex
Made variants a subsection again

@@

@@

Mutable ASTs were used in the original Smalltalk Refactoring
Browser~\cite{roberts97refactoring}, as well as in
CRefactory~\cite{garrido05program} and Photran~\cite{sle2008}.  Many compilers
use mutable ASTs internally.  However, these tools have one thing in common:
the mutable AST is not accessible via any public API.  It is intended for
internal use only, by developers who should be better equipped to handle all of
the caveats.

>>>>

\subsection{Basic Forces}

There are several basic forces at work in this problem:

@@

Traditionally, program syntax is made available through abstract syntax trees.

@@

Mutable ASTs were used in the original Smalltalk Refactoring
Browser~\cite{roberts97refactoring}, as well as in
CRefactory~\cite{garrido05program} and Photran~\cite{sle2008}.  Many compilers
use mutable ASTs internally.  However, these tools have one thing in common:
the mutable AST is not accessible via any public API.  It is intended for
internal use only, by those tools' developers who should be better equipped to handle all of
the caveats.
